---
title: "EDA"
author: "Yanan"
date: "2/9/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
setwd("/Users/doris/Desktop/Lactose/csv_3type")
```

## Reading data from 3 csv files

```{r}
data <- read.csv("preprocessed_Lactose tolerant.csv")
data_in <- read.csv("preprocessed_Lactose intolerant.csv")
data_par <- read.csv("preprocessed_Partially lactose intolerant.csv")
```

## Head of each data frames

```{r data,data_par, data_in}
head(data)
head(data_par)
head(data_in)
dim(data)
dim(data_par)
dim(data_in)
```

## Remove Gene_Info, pct_fm, pct_nm, pct_pm columns
### Slice SNPs and gene info

```{r data, data_par, data_in}
gene_data <- data[, 1:2]
```
### SLice stats of percentage for each data frame
```{r}
library(tidyverse)
mute_data <- data %>% select(pct_fm, pct_nm, pct_pm)
mute_data_par <- data_par %>% select(pct_fm, pct_nm, pct_pm)
mute_data_in <- data_in %>% select(pct_fm, pct_nm, pct_pm)
head(mute_data)
head(mute_data_in)
head(mute_data_par)
```
### Remove unrelative columns
```{r}
data = subset(data, select = -c(Gene_info, pct_fm, pct_nm, pct_pm) )
data_par = subset(data_par, select = -c(Gene_info, pct_fm, pct_nm, pct_pm) )
data_in = subset(data_in, select = -c(Gene_info, pct_fm, pct_nm, pct_pm) )
head(data)
```
## Transpose of each data frames
### Transpose of tolerant data frame

```{r data}
data1 <- data
rowames <- as.vector(data1[, 1])
data1$Rsid <- NULL
data1_t<- as.data.frame(t(data1))
colnames(data1_t) <- c(rowames)
head(data1_t)
```
### Transpose of partially tolerant data frame

```{r}
data1_par <- data_par
rownames <- as.vector(data1_par[, 1])
data1_par$Rsid <- NULL
data1_par_t<- as.data.frame(t(data1_par))
colnames(data1_par_t) <- c(rownames)
head(data1_par_t)
```
### Transpose of intolerant data frame

```{r}
data1_in <- data_in
rownames <- as.vector(data1_in[, 1])
data1_in$Rsid <- NULL
data1_in_t<- as.data.frame(t(data1_in))
colnames(data1_in_t) <- c(rownames)
head(data1_in_t)
```

## Combine data and add another column "Tolerance" 0 as intolerant, 1 as partial, 2 as tolerant
```{r}
data_addCol <- data1_t
data_parAddCol <- data1_par_t
data_inAddCol <- data1_in_t
data_addCol$tolerance = 2
data_parAddCol$tolerance = 1
data_inAddCol$tolerance = 0
```
```{r}
comb <- rbind(data_parAddCol, data_inAddCol)
comb <- rbind(data_addCol, comb)
```
```{r}
head(comb)
```
## Analysis
```{r}
tempdata<- data1_in_t
temp<- apply(tempdata, 2, function(x) length(unique(x)))
```
```{r}
temp[11]
```